Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-02 man/figures/resilience_long_term.Rmd
add gam
get nls

@@

@@

plot(sdf$d_severity, sdf$rs_mean_mean, pch=19)
lines(d$sev, predict(mod, list(sev = d$sev)))

>>>>

library("mgcv")
library("rcompanion")
mg <- gam(rs~s(sev), data=d)
summary(mg)

po <- nls(rs ~ exp.eq(sev, a, b), data = d, start = list(a = .02, b = -.07))

p <- nls(rs ~ a*exp(b*sev), data=d, start = list(a = 0.81, b = 0.021))

plot(d$sev, d$rs, pch=19)
x <- seq(5,25, 0.1)
y <- predict(p, list(sev=x))
lines(x, y)
abline(lm(d$rs~d$sev), col="red")

@@

# exploring
plot(d$sev, d$rs, pch=19, xlim=c(0,25), ylim=c(0.2, 1.6))

# try exponential 
f <- as.formula(rs ~ a*exp(b*sev))
preview(f, data = d, start = list(a = 0.8, b=0.019))

nls(f, data = d, start = list(a = 0.75, b=-0.019))

summary(mo)
nd <- expand.grid(rs=seq(0.4,1.6, by=0.1),
                  sev=seq(5,25, by=1))

lines(d$sev, predict(m, nd))

lines(nd$sev, predict(m, nd))

library("FlexParamCurve")

#modpar(posneg.data$age,posneg.data$mass,pn.options = "myoptions.1")

modpar(d$sev, d$rs, pn.options = "myoptions.1")

modcompare <- pn.mod.compare(d$sev, d$rs, d$id, pn.options = "myoptions.1")
modstep <-  pn.modselect.step(d$sev, d$rs, d$id,existing = TRUE, pn.options = "myoptions.1")

posneg.modstep <- pn.modselect.step(posneg.data$age, posneg.data$mass, posneg.data$id, existing = TRUE, pn.options = "myoptions.1")
  #existing = TRUE used to avoid refitting existing nlsList models

@@

g <- gam(rs~s(sev), data=d)

plot(g)

library
